BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2015-03-25 Paper/D5.5/D5.5.tex
Small fixes to deliverable.
Version 0.3.

\bibliographystyle{plain}
\begin{document}
\devnum{5.5}
\title{BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications}
\version{0.2}
\deadline{18}
\level{RE}
\nature{Report}
\coordinator{CNRS}
\contributors{Thierry Deutsch, Luigi Genovese, Jean-François Méhaut, Kevin Pouget, Brice Videau}
\reviewers{None}
\keywords{BOAST, Deliverable}

@@

\begin{changelog}
\change{0.1}{Initial version of the deliverable}
\change{0.2}{First version sent to reviewers}
\end{changelog}

@@

What we want is computing kernels that are:
\begin{itemize}
\item Written in a \emph{portable} manner,
\item Written in a way that raise developer \emph{productivity},
\item Written to present good \emph{performance}.
\end{itemize}

>>>>

\bibliographystyle{plain}
\begin{document}
\devnum{5.5}
\title{BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications}
\version{0.3}
\deadline{18}
\level{RE}
\nature{Report}
\coordinator{CNRS}
\contributors{Thierry Deutsch (CEA), Luigi Genovese (CEA), Jean-François Méhaut (UJF), Kevin Pouget (CNRS), Brice Videau (CNRS)}
\reviewers{Olivier Aumage (INRIA), Frédéric Desprez (INRIA)}
\keywords{BOAST, Deliverable}

@@

\begin{changelog}
\change{0.1}{Initial version of the deliverable}
\change{0.2}{First version sent to reviewers}
\change{0.3}{With corrections from reviewers}
\end{changelog}

@@

What we want is computing kernels that are:
\begin{itemize}
\item Written in a \emph{portable} manner,
\item Written in a way that raises developer \emph{productivity},
\item Written to present good \emph{performance}.
\end{itemize}
